Randomization Examples using `okcupiddata` `profiles` data

### 2018-03-08 inst/doc/profiles_examples.Rmd
Update pkgdown and vignettes

```{r include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 5, cache = TRUE) 
```

@@

```{r message=FALSE, warning=FALSE}
library(okcupiddata)
library(stringr)
library(infer)
set.seed(2017)
prof_small <- profiles %>% 
  dplyr::sample_n(size = 500) %>% 
  dplyr::mutate(city = dplyr::case_when(
    str_detect(location, "san fran") ~ "san fran",
    !str_detect(location, "san fran") ~ "not san fran"
  )) %>% 
  dplyr::select(age, sex, city, drugs, height, status)
```

@@

```{r}
prof_small %>%
  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
  hypothesize(null = "point", med = 55) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "median") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(response = sex) %>% # alt: sex ~ NULL (or sex ~ 1)
  hypothesize(null = "point", p = c("m" = .65)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "prop") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(sex ~ city) %>% # alt: response = sex, explanatory = vs
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in props") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means") %>% 
  visualize()
```

One numerical variable one categorical (2 levels) (diff in medians)

```{r}
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(response = sex) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "prop", success = "f") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(age ~ sex) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(sex ~ city) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in props") %>% 
  visualize()
```

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
```

# Note

The `okcupiddata` is thought by some to be controversial. Its use here is only
to check for a variety of different variable types and levels. It will remain only in this
"cutting edge" version of the package as we continue to add and test examples.

@@

```{r message=FALSE, warning=FALSE}
library(okcupiddata)
library(stringr)
library(infer)
set.seed(2017)
prof_small <- profiles %>% 
  na.omit() %>% 
  dplyr::sample_n(size = 500) %>% 
  dplyr::mutate(city = dplyr::case_when(
    str_detect(location, "san fran") ~ "san fran",
    !str_detect(location, "san fran") ~ "not san fran"
  )) %>% 
  dplyr::select(age, sex, city, drugs, height, status)
```

@@

```{r}
prof_small %>%
  specify(response = age) %>% # alt: age ~ NULL
  hypothesize(null = "point", med = 55) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "median") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(response = sex, success = "m") %>%
  hypothesize(null = "point", p = c("m" = .65)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "prop") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(sex ~ city, success = "m") %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
  visualize()
```

@@

One numerical variable, one categorical (2 levels) (diff in means)

```{r}
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("m", "f")) %>% 
  visualize()
```

One numerical variable, one categorical (2 levels) (diff in medians)

```{r}
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians", order = c("m", "f")) %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(response = sex, success = "f") %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "prop") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(age ~ sex) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("m", "f")) %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(sex ~ city, success = "m") %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
  visualize()
```
